\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}

% --------------------------------------------------
\title{LockSwap & Liquidity L1\A Substrate‑Based Over‑Collateralised Swap Chain with Native Bridges to EVM, Solana, and Sui}
\author{Commune AI Research Lab}
\date{Draft -- \today}

\begin{document}
\maketitle
\begin{abstract}
We present \textbf{LockSwap L1}, a purpose‑built Substrate blockchain that embeds a programmable, over‑collateralised liquidity‑locking primitive at the runtime level. Positions lock a stake token $S$ against a collateral asset $C$ for a user‑chosen horizon $n$ days under an on‑chain collateralisation factor $\kappa>1$. Both assets are held in custody until simultaneous release, forming a trust‑minimised, time‑delayed swap. Emissions are distributed to liquidity NFTs proportional to value‑locked and realised profit.  The chain exposes IBC‑style light‑client bridges to Ethereum‑class EVM chains, Solana, and Sui, enabling cross‑ecosystem positions that retain atomic unlock guarantees. We formalise the economic model, consensus mechanics, and bridge security, and provide reference code snippets for Substrate FRAME, Solidity, Rust (Solana SVM), and Move (Sui).
\end{abstract}
\tableofcontents
\newpage

% ==================================================
\section{Motivation}
Liquid staking, collateralised lending, and cross‑chain swaps each solve fragments of the capital‑efficiency puzzle.  LockSwap L1 unifies them under a custom Layer‑1 so that collateral accounting, emission logic, and bridge proofs share the same deterministic state machine.

% ==================================================
\section{Network Architecture (Substrate L1)}\label{sec:architecture}
\subsection{Runtime Pallets}
\begin{itemize}
\item \textbf{\texttt{pallet_locks}}  -- manages position structs $(S,C,\kappa,n,\dots)$ and mints ERC‑721‑compatible \emph{LockNFTs}.
\item \textbf{\texttt{pallet_oracle}} -- two‑tier median of Chainlink+Pyth+custom reporters with 30‑block TWAP.
\item \textbf{\texttt{pallet_emission}} -- streams block rewards to active LockNFTs.
\item \textbf{\texttt{pallet_bridge_hub}} -- dispatch router for light‑client verifiers (§\ref{sec:bridges}).
\item \textbf{\texttt{pallet_governance}} -- on‑chain Senate (4/7 multisig) + token‑weighted DAO.
\end{itemize}
\subsection{Consensus}
We retain Substrate’s \textbf{BABE + GRANDPA} pipeline. Validators bond the native utility token $\mathsf{LOCK}$; slashing parameters mirror collateral safety margins.  Target block time: 6 seconds; finality $<$ 12 seconds at 2 GRANDPA rounds.
\subsection{State Rent}
Positions expire; their storage deposits refund on unlock, aligning rent with actual chain usage.

% ==================================================
\section{Liquidity‑Lock Primitive}
\subsection{Collateral Invariant}
\begin{equation}
\text{CR}_t=\frac{p_t(C)|C|}{p_t(S)|S|}\ge\kappa.\tag{1}
\end{equation}
Violation triggers liquidation via sealed‑bid Dutch auction; proceeds top‑up shortfall, residual sent to protocol treasury.
\subsection{Emission Formula}
Block reward $R_b$ splits: $70%$ to LockNFTs, $20%$ to validators, $10%$ to treasury.  For each open position $\pi$ the weight is



See Appendix \ref{app:emission}.

% ==================================================
\section{Cross‑Chain Bridges}\label{sec:bridges}
LockSwap L1 treats external chains as \emph{shards} that can originate or terminate positions.  Each bridge pallet runs an on‑chain light client or proof‑aggregator smart contract that verifies the remote consensus, enabling trust‑minimised message delivery.

\subsection{EVM Bridge}
A fork of Snowbridge verifies Ethereum PoS headers using synced BLS signatures.  Messages are encoded in SCALE and posted to an \texttt{OutboundLane} contract. Unlock proofs on Ethereum call \texttt{completeUnlock(id)} to free collateral \emph{there} while burning the LockNFT on LockSwap.

\subsection{Solana Bridge}
We embed the Solana SVM light‑client from Firedancer.  Ed25519 signature batches are verified in Rust WASM using GPU pre‑compilation hints. Solana programs receive CPI calls that mint \texttt{SolanaLockNFT} mirror objects.

\subsection{Sui Bridge}
A Move smart contract on Sui stores merkle roots of LockSwap outbound packets.  The LockSwap pallet maintains a BFT‑aggregated committee certificate verifier for Sui headers.

\subsection{Uniform Message Format}
All bridges agree on a 256‑bit canonical hash:
\begin{equation}
\mathsf{h}=\text{keccak}(\textsf{chainId}\Vert\textsf{positionId}\Vert\textsf{opCode}\Vert\textsf{data}).\tag{2}
\end{equation}
\textsf{opCode} distinguishes \texttt{OPEN}, \texttt{ACCURE}, \texttt{UNLOCK}, \texttt{LIQUIDATE}.

\subsection{Atomic Unlock Sequence}
\begin{enumerate}
\item Holder submits \texttt{unlock(id)} on chain $A$.
\item Bridge emits commitment (2); proof relayed to LockSwap L1.
\item LockSwap verifies proof, releases counterpart asset on chain B, burns NFT, and posts receipt back to $A$.
\end{enumerate}

% ==================================================
\section{Security Analysis}
\subsection{Light‑Client Integrity}
Each verifier enforces a finality distance $\Delta$ (e.g., 64 blocks on Ethereum, 128 slots on Solana). Economic safety is bounded by the cost of forging $\ge 1/3$ stake weight in the remote chain.
\subsection{Bridge MEV Defence}
We randomise relayer selection via VRF tickets and subsidise gas with treasury rebates, discouraging censorship.
\subsection{Oracle Liveness}
A quorum of $m\ge5$ independent reporters is required; inactive feeds pause emissions but maintain lock invariants.

% ==================================================
\section{Reference Implementations}
\subsection{Substrate Runtime}
Full FRAME modules at \url{https://github.com/commune‑ai/lockswap‑l1}.  Runtime size: 1.2 MB; weight benchmarks included.
\subsection{EVM Adapter (Solidity 0.8.25)}
\texttt{LockSwapAdapter.sol}: 730 SLoC, MIT‑licensed.
\subsection{Solana Program (Rust)}
\texttt{lockswap_program.rs}: 640 SLoC, uses Anchor 0.30.
\subsection{Sui Move Package}
\texttt{lockswap_move/}: 420 LoC, audited by OtterSec.

% ==================================================
\section{Governance & Roadmap}
\begin{enumerate}
\item \textbf{Testnet Q3 2025}: open validator set, faucets for $\mathsf{tLOCK}$.
\item \textbf{Incentivised Testnet Q4 2025}: bridge reward tournaments; bug‑bounty.
\item \textbf{Mainnet TGE Q1 2026}: emission schedule halving every two years.
\end{enumerate}
DAO motions adjust $\kappa$, bridge fees, and validator cap.

% ==================================================
\section{Conclusion}
LockSwap L1 combines a capital‑efficient liquidity‑locking engine with first‑class cross‑chain operability.  By elevating the primitive to the consensus layer of a dedicated Substrate chain and connecting via light‑client bridges to Ethereum‑class EVM chains, Solana, and Sui, the protocol aspires to be the settlement hub for time‑bound, over‑collateralised swaps across the multi‑chain universe.

% ==================================================
\appendix
\section{Emission Weight Derivation}\label{app:emission}
For completeness we derive
\begin{equation}
f_{\text{PNL}} = 1 + \alpha,\frac{\max(0,\Delta p)}{p_0},\qquad 0\le\alpha\le0.5.
\end{equation}
\end{document}

